Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-04-08 thirdPaper/draft/typeConeAssociahedra.tex
start intro

% math special letters
\newcommand{\R}{\mathbb{R}} % reals
\newcommand{\Q}{\mathbb{Q}} % rationals
\newcommand{\N}{\mathbb{N}} % naturals
\newcommand{\Z}{\mathbb{Z}} % integers
\newcommand{\C}{\mathbb{C}} % complex
\newcommand{\I}{\mathbb{I}} % set of integers
\newcommand{\HH}{\mathbb{H}} % hyperplane
\newcommand{\K}{k} % field
\newcommand{\fA}{\mathfrak{A}} % alternating group
\newcommand{\fS}{\mathfrak{S}} % symmetric group
\newcommand{\cA}{\mathcal{A}} % algebra
\newcommand{\cC}{\mathcal{C}} % collection
\newcommand{\cS}{\mathcal{S}} % ground set
\newcommand{\uR}{\underline{R}} % underline set
\newcommand{\uS}{\underline{S}} % underline set
\newcommand{\uT}{\underline{T}} % underline set
\newcommand{\oS}{\overline{S}} % overline set
\newcommand{\ucS}{\underline{\cS}} % underline ground set
\renewcommand{\b}[1]{{\boldsymbol{#1}}} % bold letters
\newcommand{\h}{\widehat} % hat letters

@@

We explain recent results of~\cite{BazierMatteDouvilleMousavandThomasYildirim}. Some advantages of our approach are:
\begin{itemize}
\item We manage to extend their results to other families of $\b{g}$-vector fans: first to all $\b{g}$-vector fans of finite type cluster algebras acyclic or not (whose polytopality was only proved recently in~\cite{HohlwegPilaudStella}), then to all $\b{g}$-vector fans of the $\tau$-tilting finite gentle algebras (whose polytopality was proved recently in~\cite{PaluPilaudPlamondon-nonkissing}), and finally to the nested fans of graph associahedra (whose polytopality was studied in~\cite{CarrDevadoss, Devadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}).
\item We have a simpler proof, only based on the transformation between the classical descriptions of a polytope of the form~$\set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$ and~$\set{\b{z} \in \R^N}{\b{K}\b{z} = \b{K}\b{h} \text{ and } \b{z} \ge 0}$ (this transformation is standard in optimization). In particular, we do not need to consider only rational polytopes and pass to the limit to deal with all real descriptions.
\item We observe that we obtain all realizations of the $\b{g}$-vector fans of the considered families.
\end{itemize}

@@

Although we will only treat with simplicial fans, for completeness, note that \cref{prop:characterizationPolytopalFan} and \cref{def:typecone} can be easily adapted to non-simplicial fans. For an arbitrary complete fan, it suffices to consider consider any simplicial refinement, and set some of the strict inequalities of the definition of the type cone to equality.
\begin{proposition}
 \label{prop:non-simplicial}
 Let $\Fan'$ be a complete fan that coarsens the essential complete simplicial fan~$\Fan$.
 The \defn{type-cone}~$\typeCone(\Fan')$ of all $\Fan'$-admissible height vectors~$\b{h}$ is
 \begin{align*}
 \typeCone(\Fan) 
%  & \eqdef \set{\b{h} \in \R^N}{\Fan \text{ is the normal fan of } P_\b{h}} \\
& = \left\{\b{h} \in \R^N\;\middle|\;
\begin{array}{ll}
 \sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} = 0
 & \begin{array}{l} \text{for any adjacent maximal cones} \\ \text{$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ \textbf{belonging}}\\\text{to the same maximal cone of $\Fan'$; and}\end{array}
\\\\
\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} > 0
 & \begin{array}{l} \text{for any adjacent maximal cones} \\ \text{$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ \textbf{not belonging}}\\\text{to the same maximal cone of $\Fan'$}\end{array}
\end{array}
 \right\}.
 \end{align*}
\end{proposition}
\arnau{should add proof or citation}

@@

We now focus on the normal fan~$\gvectorFan[n]$ of~$\Asso[n]$.
Since~$\Asso[n]$ leaves in a hyperplane of~$\R^{n+1}$, so does its normal fan.
Let~$\HH \eqdef \bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} x_\ell = 0}$ and~$\pi : \R^{n+1} \to \HH$ denote the orthogonal projection.

@@

These fans are illustrated in \cref{fig:lodayFans} in dimension~$2$ and~$3$.
Let us also recall the linear dependencies in this fan and observe that it has the unique exchange property discussed in \cref{subsec:uniqueExchangeProperty}.
From now on, we use the convention that~$\gvector{a,b} = 0$ when~$(a,b)$ is a boundary edge of the $(n+3)$-gon.

@@

\begin{example}
Consider the fan~$\gvectorFan[2]$ and~$\gvectorFan[3]$ illustrated in \cref{fig:lodayFans}.
The type cone of~$\gvectorFan[2]$ lives in~$\R^5$ and has a linearity space of dimension~$2$.
It has $3$ facet defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititesAsso}\,(left).

@@

\noindent
The type cone of~$\gvectorFan[2]$ lives in~$\R^9$ and has a linearity space of dimension~$3$.
It has $6$ facet defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititesAsso}\,(left).

\[
\begin{array}{r|cccccccccc}
\text{diagonals} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB1}}  & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB2}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB3}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB4}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB5}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB6}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB7}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB8}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB9}} \\[.3cm]
\text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{1}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{-1}{1}{0} & \compactVectorT{0}{-1}{1} & \compactVectorT{-1}{0}{1} & \compactVectorT{-1}{0}{0} & \compactVectorT{0}{-1}{0} & \compactVectorT{0}{0}{-1} \\[.6cm]
%\text{linearity}	& 0 & 1 & 0 & 1 & 0 & -1 & 0 & -1 & 0 \\
%\text{space}		& 0 & 1 & 1 & 1 & 1 & 0 & 0 & -1 & -1 \\
%					& 1 & 1 & 1 & 0 & 0 & 0 & -1 & -1 & -1 \\
\text{facet}		& 1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & \red \circled{A} \\
\text{defining} 	& 0 & 1 & -1 & -1 & 1 & 0 & 0 & 0 & 0 & \red \circled{B} \\
\text{inequalities}	& 0 & 0 & 1 & 0 & -1 & 0 & 1 & 0 & 0 & \red \circled{C} \\
					& 0 & 0 & 0 & 1 & -1 & 1 & 0 & 0 & 0 & \red \circled{D} \\
					& 0 & 0 & 0 & 0 & 1 & -1 & -1 & 1 & 0 & \red \circled{E} \\
					& 0 & 0 & 0 & 0 & 0 & 1 & 0 & -1 & 1 & \red \circled{F} \\[.2cm]
\end{array}
\]

@@

\begin{figure}
    \begin{adjustbox}{center}
        \begin{tikzpicture}
        	\matrix (m) [matrix of math nodes, row sep=.35cm, column sep=.2cm, nodes={anchor=center, align=center, inner sep=0pt}]{
        		& \;\includegraphics[scale=.7]{diagonalA2} & \node (b) {\red \circled{B}}; & \;\includegraphics[scale=.7]{diagonalA4} & \\
        		\;\includegraphics[scale=.7]{diagonalA1} & \node (a) {\red \circled{A}}; & \;\includegraphics[scale=.7]{diagonalA3} & \node (c) {\red \circled{C}}; & \;\includegraphics[scale=.7]{diagonalA5} \\};
        	\draw[->] (m-2-1) -- (m-1-2);
        	\draw[->] (m-1-2) -- (m-2-3);
        	\draw[->] (m-2-3) -- (m-1-4);
        	\draw[->] (m-1-4) -- (m-2-5);
        	\draw[red] (a) -- (m-2-1);
        	\draw[red] (a) -- (m-2-3);
        	\draw[red] (a) -- (m-1-2);
        	\draw[red] (b) -- (m-1-2);
        	\draw[red] (b) -- (m-1-4);
        	\draw[red] (b) -- (m-2-3);
        	\draw[red] (c) -- (m-2-3);
        	\draw[red] (c) -- (m-2-5);
        	\draw[red] (c) -- (m-1-4);
        \end{tikzpicture}
        \quad
        \begin{tikzpicture}
        	\matrix (m) [matrix of math nodes, row sep=.35cm, column sep=.2cm, nodes={anchor=center, align=center, inner sep=0pt}]{
        		&& \;\includegraphics[scale=.7]{diagonalB3} & \node (c) {\red \circled{C}}; & \;\includegraphics[scale=.7]{diagonalB7} && \\
        		& \;\includegraphics[scale=.7]{diagonalB2} & \node (b) {\red \circled{B}}; & \;\includegraphics[scale=.7]{diagonalB5} & \node (e) {\red \circled{E}}; & \;\includegraphics[scale=.7]{diagonalB8} & \\
        		\;\includegraphics[scale=.7]{diagonalB1} & \node (a) {\red \circled{A}}; & \;\includegraphics[scale=.7]{diagonalB4} & \node (d) {\red \circled{D}}; & \;\includegraphics[scale=.7]{diagonalB6} & \node (f) {\red \circled{F}}; & \;\includegraphics[scale=.7]{diagonalB9} \\};
        	\draw[->] (m-3-1) -- (m-2-2);
        	\draw[->] (m-2-2) -- (m-1-3);
        	\draw[->] (m-2-2) -- (m-3-3);
        	\draw[->] (m-1-3) -- (m-2-4);
        	\draw[->] (m-3-3) -- (m-2-4);
        	\draw[->] (m-2-4) -- (m-1-5);
        	\draw[->] (m-2-4) -- (m-3-5);
        	\draw[->] (m-1-5) -- (m-2-6);
        	\draw[->] (m-3-5) -- (m-2-6);
        	\draw[->] (m-2-6) -- (m-3-7);
        	\draw[red] (a) -- (m-3-1);
        	\draw[red] (a) -- (m-3-3);
        	\draw[red] (a) -- (m-2-2);
        	\draw[red] (b) -- (m-2-2);
        	\draw[red] (b) -- (m-2-4);
        	\draw[red] (b) -- (m-1-3);
        	\draw[red] (b) -- (m-3-3);
        	\draw[red] (c) -- (m-1-3);
        	\draw[red] (c) -- (m-1-5);
        	\draw[red] (c) -- (m-2-4);
        	\draw[red] (d) -- (m-3-3);
        	\draw[red] (d) -- (m-3-5);
        	\draw[red] (d) -- (m-2-4);
        	\draw[red] (e) -- (m-2-4);
        	\draw[red] (e) -- (m-2-6);
        	\draw[red] (e) -- (m-1-5);
        	\draw[red] (e) -- (m-3-5);
        	\draw[red] (f) -- (m-3-5);
        	\draw[red] (f) -- (m-3-7);
        	\draw[red] (f) -- (m-2-6);
        \end{tikzpicture}
    \end{adjustbox}
	\caption{The facet defining inequalities of the type cone~$\typeCone(\gvectorFan[n])$ correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso}. See \cref{subsec:typeConeCA,sec:clusterCategories} for a representation theoretic \mbox{interpretation}.}
	\label{fig:labelFacetDefiningInequalititesAsso}
\end{figure}
\end{example}

We now describe the facets of this type cone~$\typeCone(\gvectorFan[n])$.

@@

\begin{corollary}[{\cite[Sect.~3.2]{ArkaniHamedBaiHeYan}}]
For~$n \in \N$, define~$X(n) \eqdef \set{(a,b)}{0 \le a < b \le n+2}$ and~$Y(n) \eqdef \set{(a,b)}{0 \le a < b-2 \le n}$.
Then for any~$\b{\ell} \in \R_{>0}^{Y(n)}$, the polytope
\[
R_\b{\ell}(n) \eqdef \set{\b{z} \in \R^{X(n)}}{\begin{array}{l} \b{z} \ge 0, \quad \b{z}_{(0,n+2)} = 0 \quad\text{and}\quad \b{z}_{(a,a+1)} = 0 \text{ for all } 0 \le a \le n+1 \\ \b{z}_{(a,b-1)} + \b{z}_{(a+1,b)} - \b{z}_{(a,b)} - \b{z}_{(a+1,b-1)} = \b{\ell}_{(a,b)} \text{ for all } (a,b) \in Y(n) \end{array}}
%\bigset{\b{z} \in \R^{X(n)}}{\b{z} \ge 0, \; \b{z}_{1,n+1} = 0 \text{ and } \b{z}_{i,j} + \b{z}_{i+1,j+1} - \b{z}_{i,j+1} - \b{z}_{i+1,j} = \b{\ell}_{i,j} \text{ for } (i,j) \in X(n-1)}
\]
is an $n$-dimensional associahedron.
\end{corollary}

@@

In this section, we need to restrict even further the family of gentle quivers we consider.
\vincent{rephrase}

@@

>>>>

% math special letters
\newcommand{\R}{\mathbb{R}} % reals
\newcommand{\Q}{\mathbb{Q}} % rationals
\newcommand{\N}{\mathbb{N}} % naturals
\newcommand{\Z}{\mathbb{Z}} % integers
\newcommand{\C}{\mathbb{C}} % complex
\newcommand{\I}{\mathbb{I}} % set of integers
\newcommand{\HH}{\mathbb{H}} % hyperplane
\newcommand{\K}{k} % field
\newcommand{\f}[1]{{\mathfrak{#1}}} % mathfrak letters
\renewcommand{\c}[1]{{\mathcal{#1}}} % call letters
\renewcommand{\b}[1]{{\boldsymbol{#1}}} % bold letters
\newcommand{\h}{\widehat} % hat letters

@@

\newpage

The associahedron is a ``mythical polytope'' \cite{Haiman} whose facial structure encodes Catalan families: its vertices correspond to parenthesizations of a non-associative product, triangulations of a convex polygon, or binary trees; its edges correspond to applications of the associativity rule, diagonal flips, or edge rotations; and in general its faces correspond to partial parenthesizations, diagonal dissections, or Schr\"oder trees.
Its combinatorial and topological structure was introduced in early works of D.~Tamari~\cite{Tamari} and J.~Stasheff~\cite{Stasheff}, and a first polytopal model was realized by J.~Milnor for the PhD defense of the latter.
The first systematic polytopal realizations were constructed by M.~Haiman~\cite{Haiman} and C.~Lee~\cite{Lee}.
Since then, the associahedron has been largely ``demystified'' with several polytopal constructions...
%~\cite{Loday, HohlwegLange, LangePilaud}.
%See~\cite{CeballosSantosZiegler} for a survey on these constructions.
% and generalizations to secondary and fiber polytopes~\cite{GelfandKapranovZelevinsky, BilleraFillimanSturmfels}, to pseudotriangulation polytopes~\cite{RoteSantosStreinu-polytope}, to graph associahedra and nestohedra~\cite{CarrDevadoss, Devadoss, Postnikov, FeichtnerSturmfels, Zelevinsky, Pilaud-removahedra}, to cluster complexes and generalized associahedra~\cite{FominZelevinsky-YSystems, FominZelevinsky-ClusterAlgebrasI, FominZelevinsky-ClusterAlgebrasII, ChapotonFominZelevinsky, HohlwegLangeThomas, Stella, Hohlweg, HohlwegPilaudStella}, to brick polytopes~\cite{PilaudSantos-brickPolytope, PilaudStump-brickPolytope}, to quotientopes~\cite{Reading-latticeCongruences, Reading-CambrianLattices, PilaudSantos-quotientopes}, etc.

The associahedron appears as a fundamental structure in several mathematical theories, such as moduli spaces and topology~\cite{Stasheff, Keller-AinfinityAlgebras}, operads and rewriting theory~\cite{}, combinatorial Hopf algebras~\cite{LodayRonco, ChatelPilaud, Pilaud-brickAlgebra}, diagonal harmonics~\cite{}, mathematical physics~\cite{ArkaniHamedBaiHeYan}, etc.
Another striking illustration of the ubiquity of the associahedron lies in the theory of cluster algebras introduced by S.~Fomin and A.~Zelevinsky in~\cite{FominZelevinsky-ClusterAlgebrasI} with motivation coming from total positivity and canonical bases.
Cluster algebras are commutative rings generated by variables obtained from an initial seed by the discrete dynamical process of seed mutations.
Finite type cluster algebras, whose mutation graph is finite, were classified in~\cite{FominZelevinsky-ClusterAlgebrasII} using the Cartan-Killing classification for crystallographic root systems.
Finite type cluster complexes were geometrically realized first by F.~Chapoton, S.~Fomin and A.~Zelevinsky~\cite{ChapotonFominZelevinsky} based on the $\b{d}$-vector fans~\cite{FominZelevinsky-YSystems, FominZelevinsky-ClusterAlgebrasII}, then by~C.~Hohlweg, C.~Lange and H.~Thomas~\cite{HohlwegLangeThomas} based on the Cambrian fans~\cite{Reading-CambrianLattices, ReadingSpeyer}, and finally by C.~Hohlweg, V.~Pilaud and S.~Stella~\cite{HohlwegPilaudStella} based on the $\b{g}$-vector fans~\cite{FominZelevinsky-ClusterAlgebrasIV} with respect to an arbitrary initial seed.
The resulting polytopes are known as generalized associahedra, and the classical associahedra corresponds to the cluster algebras of type~$A$.

This paper focuses on a recent construction of the associahedron that appeared in mathematical physics.
Motivated by the prediction of the behavior of scattering particules, N.~Arkani-Hamed, Y.~Bai, S.~He, and G.~Yan recently described in~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} the kinetic associahedron.
It is a class of polytopal realizations of the classical associahedron obtained as sections of a high-dimensional positive orthant with well-chosen affine subspaces.
This construction provides a large degree of freedom in the choice of the parameters defining these affine subspaces and produces all polytopes whose normal fan is affinely equivalent to that of J.-L.~Loday's associahedron~\cite{Loday} (see \cref{subsec:typeConeAsso}).
These realizations were then extended by V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Yildirim~\cite{BazierMatteDouvilleMousavandThomasYildirim} in the context of finite type cluster algebras using tools from representation theory of quivers.
More precisely, they fix a finite type cluster algebra~$\c{A}$ and consider the real euclidean space~$\R^\c{V}$ indexed by the set~$\c{V}$ of cluster variables of~$\c{A}$.
Starting from an acyclic initial seed~$\seed_\circ$, they consider a certain set~$\c{M}$ of mesh relations and compute the corresponding linear relations between the $\b{g}$-vectors, interpreted as linear spaces in~$\R^\c{V}$.
Finally, they perturb these mesh linear spaces by a collection~$\b{\ell} \in \R^{\c{M}}$ of positive constants and intersect the resulting perturbed affine mesh relations with the positive orthant of~$\R^\c{V}$ (see \cref{subsec:typeConeCA}).
They show that the resulting polytope is always a generalized associahedron, and that its normal fan is the $\b{g}$-vector fan of~$\c{A}$ with respect to the initial acyclic seed~$\seed_\circ$.
A by-product of their construction is that the space of all polytopal realizations of the $\b{g}$-vector fan of~$\c{A}$ with respect to the initial acyclic seed~$\seed_\circ$ is a simplicial cone.

In this paper, we revisit, extend and explore further this construction using a different approach.
Given a complete simplicial fan~$\Fan$, we consider its space~$\typeCone(\Fan)$ of polytopal realizations, called type-cone of~$\Fan$ in~\cite{McMullen-typeCone}.
This type-cone is known to be a polyhedral cone defined by a collection of inequalities corresponding to the linear dependences among the rays of~$\Fan$ contained in pairs of adjacent maximal cones of~$\Fan$.
Our approach is based on a simple but crucial observation: if the type-cone~$\typeCone(\Fan)$ is a simplicial cone, then all polytopal realizations of~$\Fan$ can be described as sections of a high dimensional positive orthant with a collection of affine subspaces corresponding to the facets of~$\typeCone(\Fan)$ (see \cref{coro:simplicialTypeCone}).
To prove that the type-cone~$\typeCone(\Fan)$ is simplicial, we just need to identify which pairs of adjacent maximal cones of~$\Fan$ correspond to the facets of~$\typeCone(\Fan)$ and to show that the corresponding linear dependences among their rays positively span the linear dependence among the rays of any pair of adjacent maximal cones of~$\Fan$.

%
%
%Their proof, based on representation theory of quivers, is subtle: on the one hand, only simply-laced types are explicitly treated and the remaining finite type are argued by folding; on the other hand, the technique requires to work with rational perturbations~$\b{\ell}$ and to conclude for arbitrary real perturbations by an approximation argument.

%Is the realization space connected?

%We explain recent results of~\cite{BazierMatteDouvilleMousavandThomasYildirim}. Some advantages of our approach are:
%\begin{itemize}
%\item We manage to extend their results to other families of $\b{g}$-vector fans: first to all $\b{g}$-vector fans of finite type cluster algebras acyclic or not (whose polytopality was only proved recently in~\cite{HohlwegPilaudStella}), then to all $\b{g}$-vector fans of the $\tau$-tilting finite gentle algebras (whose polytopality was proved recently in~\cite{PaluPilaudPlamondon-nonkissing}), and finally to the nested fans of graph associahedra (whose polytopality was studied in~\cite{CarrDevadoss, Devadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}).
%\item We have a simpler proof, only based on the transformation between the classical descriptions of a polytope of the form~$\set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$ and~$\set{\b{z} \in \R^N}{\b{K}\b{z} = \b{K}\b{h} \text{ and } \b{z} \ge 0}$ (this transformation is standard in optimization). In particular, we do not need to consider only rational polytopes and pass to the limit to deal with all real descriptions.
%\item We observe that we obtain all realizations of the $\b{g}$-vector fans of the considered families.
%\end{itemize}

@@

Although we will only treat with simplicial fans, for completeness, note that \cref{prop:characterizationPolytopalFan} and \cref{def:typecone} can be easily adapted to non-simplicial fans. For an arbitrary complete fan, it suffices to consider any simplicial refinement, and set some of the strict inequalities of the definition of the type cone to equality.
\begin{proposition}
 \label{prop:non-simplicial}
 Let $\Fan'$ be a complete fan that coarsens the essential complete simplicial fan~$\Fan$.
 The \defn{type-cone}~$\typeCone(\Fan')$ of all $\Fan'$-admissible height vectors~$\b{h}$ is
 \begin{align*}
 \typeCone(\Fan) 
%  & \eqdef \set{\b{h} \in \R^N}{\Fan \text{ is the normal fan of } P_\b{h}} \\
& = \left\{\b{h} \in \R^N\;\middle|\;
\begin{array}{ll}
 \sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} = 0
 & \begin{array}{l} \text{for any adjacent maximal cones} \\ \text{$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ \textbf{belonging}}\\\text{to the same maximal cone of $\Fan'$; and}\end{array}
\\\\
\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} > 0
 & \begin{array}{l} \text{for any adjacent maximal cones} \\ \text{$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ \textbf{not belonging}}\\\text{to the same maximal cone of $\Fan'$}\end{array}
\end{array}
 \right\}.
 \end{align*}
\end{proposition}
\arnau{should add proof or citation}

@@

We now focus on the normal fan~$\gvectorFan[n]$ of~$\Asso[n]$.
Since~$\Asso[n]$ leaves in a hyperplane of~$\R^{n+1}$, so does its normal fan.
Let~$\HH \eqdef \bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} x_\ell = 0}$ and~$\pi : \R^{n+1} \to \HH$ denote the orthogonal projection.
The following fans are illustrated in \cref{fig:lodayFans} in dimension~$2$ and~$3$.

@@

Let us also recall the linear dependencies in this fan and observe that it has the unique exchange property discussed in \cref{subsec:uniqueExchangeProperty}.
From now on, we use the convention that~$\gvector{a,b} = 0$ when~$(a,b)$ is a boundary edge of the $(n+3)$-gon.

@@

\begin{example}
\label{exm:typeConeAsso}
Consider the fan~$\gvectorFan[2]$ and~$\gvectorFan[3]$ illustrated in \cref{fig:lodayFans}.
The type cone of~$\gvectorFan[2]$ lives in~$\R^5$ and has a linearity space of dimension~$2$.
It has $3$ facet defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititesAsso}\,(left).

@@

\noindent
In all our tables, we just record the coefficients of the inequalities, which are then easily reconstructed.
For instance, the inequality~$\red \circled{A}$ above is given by~$\b{h}_{\includegraphics[scale=.3]{diagonalA1}} + \b{h}_{\includegraphics[scale=.3]{diagonalA3}} > \b{h}_{\includegraphics[scale=.3]{diagonalA2}}$.

The type cone of~$\gvectorFan[2]$ lives in~$\R^9$ and has a linearity space of dimension~$3$.
It has $6$ facet defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititesAsso}\,(left).

\[
\begin{array}{r|cccccccccc}
\text{diagonals} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB1}}  & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB2}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB3}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB4}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB5}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB6}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB7}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB8}} & \raisebox{-.25cm}{\;\includegraphics[scale=.7]{diagonalB9}} \\[.3cm]
\text{$\b{g}$-vectors} & \compactVectorT{1}{0}{0} & \compactVectorT{0}{1}{0} & \compactVectorT{0}{0}{1} & \compactVectorT{-1}{1}{0} & \compactVectorT{0}{-1}{1} & \compactVectorT{-1}{0}{1} & \compactVectorT{-1}{0}{0} & \compactVectorT{0}{-1}{0} & \compactVectorT{0}{0}{-1} \\[.6cm]
\text{facet}		& 1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & \red \circled{A} \\
\text{defining} 	& 0 & 1 & -1 & -1 & 1 & 0 & 0 & 0 & 0 & \red \circled{B} \\
\text{inequalities}	& 0 & 0 & 1 & 0 & -1 & 0 & 1 & 0 & 0 & \red \circled{C} \\
					& 0 & 0 & 0 & 1 & -1 & 1 & 0 & 0 & 0 & \red \circled{D} \\
					& 0 & 0 & 0 & 0 & 1 & -1 & -1 & 1 & 0 & \red \circled{E} \\
					& 0 & 0 & 0 & 0 & 0 & 1 & 0 & -1 & 1 & \red \circled{F} \\[.2cm]
\end{array}
\]

@@

\begin{figure}[h]
    \begin{adjustbox}{center}
        \begin{tikzpicture}
        	\matrix (m) [matrix of math nodes, row sep=.35cm, column sep=.2cm, nodes={anchor=center, align=center, inner sep=0pt}]{
        		& \;\includegraphics[scale=.7]{diagonalA2} & \node (b) {\red \circled{B}}; & \;\includegraphics[scale=.7]{diagonalA4} & \\
        		\;\includegraphics[scale=.7]{diagonalA1} & \node (a) {\red \circled{A}}; & \;\includegraphics[scale=.7]{diagonalA3} & \node (c) {\red \circled{C}}; & \;\includegraphics[scale=.7]{diagonalA5} \\};
        	\draw[->] (m-2-1) -- (m-1-2);
        	\draw[->] (m-1-2) -- (m-2-3);
        	\draw[->] (m-2-3) -- (m-1-4);
        	\draw[->] (m-1-4) -- (m-2-5);
        	\draw[red] (a) -- (m-2-1);
        	\draw[red] (a) -- (m-2-3);
        	\draw[red] (a) -- (m-1-2);
        	\draw[red] (b) -- (m-1-2);
        	\draw[red] (b) -- (m-1-4);
        	\draw[red] (b) -- (m-2-3);
        	\draw[red] (c) -- (m-2-3);
        	\draw[red] (c) -- (m-2-5);
        	\draw[red] (c) -- (m-1-4);
        \end{tikzpicture}
        \quad
        \begin{tikzpicture}
        	\matrix (m) [matrix of math nodes, row sep=.35cm, column sep=.2cm, nodes={anchor=center, align=center, inner sep=0pt}]{
        		&& \;\includegraphics[scale=.7]{diagonalB3} & \node (c) {\red \circled{C}}; & \;\includegraphics[scale=.7]{diagonalB7} && \\
        		& \;\includegraphics[scale=.7]{diagonalB2} & \node (b) {\red \circled{B}}; & \;\includegraphics[scale=.7]{diagonalB5} & \node (e) {\red \circled{E}}; & \;\includegraphics[scale=.7]{diagonalB8} & \\
        		\;\includegraphics[scale=.7]{diagonalB1} & \node (a) {\red \circled{A}}; & \;\includegraphics[scale=.7]{diagonalB4} & \node (d) {\red \circled{D}}; & \;\includegraphics[scale=.7]{diagonalB6} & \node (f) {\red \circled{F}}; & \;\includegraphics[scale=.7]{diagonalB9} \\};
        	\draw[->] (m-3-1) -- (m-2-2);
        	\draw[->] (m-2-2) -- (m-1-3);
        	\draw[->] (m-2-2) -- (m-3-3);
        	\draw[->] (m-1-3) -- (m-2-4);
        	\draw[->] (m-3-3) -- (m-2-4);
        	\draw[->] (m-2-4) -- (m-1-5);
        	\draw[->] (m-2-4) -- (m-3-5);
        	\draw[->] (m-1-5) -- (m-2-6);
        	\draw[->] (m-3-5) -- (m-2-6);
        	\draw[->] (m-2-6) -- (m-3-7);
        	\draw[red] (a) -- (m-3-1);
        	\draw[red] (a) -- (m-3-3);
        	\draw[red] (a) -- (m-2-2);
        	\draw[red] (b) -- (m-2-2);
        	\draw[red] (b) -- (m-2-4);
        	\draw[red] (b) -- (m-1-3);
        	\draw[red] (b) -- (m-3-3);
        	\draw[red] (c) -- (m-1-3);
        	\draw[red] (c) -- (m-1-5);
        	\draw[red] (c) -- (m-2-4);
        	\draw[red] (d) -- (m-3-3);
        	\draw[red] (d) -- (m-3-5);
        	\draw[red] (d) -- (m-2-4);
        	\draw[red] (e) -- (m-2-4);
        	\draw[red] (e) -- (m-2-6);
        	\draw[red] (e) -- (m-1-5);
        	\draw[red] (e) -- (m-3-5);
        	\draw[red] (f) -- (m-3-5);
        	\draw[red] (f) -- (m-3-7);
        	\draw[red] (f) -- (m-2-6);
        \end{tikzpicture}
    \end{adjustbox}
	\caption{The facet defining inequalities of the type cone~$\typeCone(\gvectorFan[n])$ correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso}. See \cref{subsec:typeConeCA,sec:clusterCategories} for a representation theoretic \mbox{interpretation}.}
	\label{fig:labelFacetDefiningInequalititesAsso}
\end{figure}
\end{example}

Motivated by \cref{exm:typeConeAsso}, we now describe the facets of this type cone~$\typeCone(\gvectorFan[n])$.

@@

\begin{corollary}[{\cite[Sect.~3.2]{ArkaniHamedBaiHeYan}}]
\label{coro:allPolytopalRealizationsAsso}
For~$n \in \N$, define~$X(n) \eqdef \set{(a,b)}{0 \le a < b \le n+2}$ and~$Y(n) \eqdef \set{(a,b)}{0 \le a < b-2 \le n}$.
Then for any~$\b{\ell} \in \R_{>0}^{Y(n)}$, the polytope
\[
R_\b{\ell}(n) \eqdef \set{\b{z} \in \R^{X(n)}}{\begin{array}{l} \b{z} \ge 0, \quad \b{z}_{(0,n+2)} = 0 \quad\text{and}\quad \b{z}_{(a,a+1)} = 0 \text{ for all } 0 \le a \le n+1 \\ \b{z}_{(a,b-1)} + \b{z}_{(a+1,b)} - \b{z}_{(a,b)} - \b{z}_{(a+1,b-1)} = \b{\ell}_{(a,b)} \text{ for all } (a,b) \in Y(n) \end{array}}
%\bigset{\b{z} \in \R^{X(n)}}{\b{z} \ge 0, \; \b{z}_{1,n+1} = 0 \text{ and } \b{z}_{i,j} + \b{z}_{i+1,j+1} - \b{z}_{i,j+1} - \b{z}_{i+1,j} = \b{\ell}_{i,j} \text{ for } (i,j) \in X(n-1)}
\]
is an $n$-dimensional associahedron, whose normal fan is~$\gvectorFan[n]$.
Moreover, the polytopes~$R_\b{\ell}(n)$ for~$\b{\ell} \in \R_{>0}^{Y(n)}$ describe all polytopal realizations of the fan~$\gvectorFan[n]$.
\end{corollary}

\vincent{Describe the rays of the type cone. They are the Minkowski basis.}

@@

In this section, we will restrict our attention to the following family of quivers.

@@

\vincent{Describe the rays of the type cone. They are the Minkowski basis.}
